% !TEX root = tracking.tex
\section{Conclusions and Future work}
In this paper we introduced FaSTrack: Fast and Safe Tracking, which is a framework for providing trajectory-independent tracking error bounds (TEB) for a tracking model, which represents an autonomous system, and a planning model, which represents a simplified model of the autonomous system.
The TEB is obtained by analyzing a pursuit-evasion game between the tracking and planning models, and obtaining the associated value function by solving a Hamilton-Jacobi (HJ) variational inequality (VI).  %When this game converges we acquire an infinite-horizon TEB, otherwise we acquire a time-varying TEB.

We demonstrated the framework's utility in three representative numerical simulations involving a 5D car model tracking a 3D car model planning using the fast sweeping method, a 10D quadrotor model tracking a 3D single integrator model planning using rapid-exploring random trees, and an 8D quadrotor model tracking a 4D double integrator planning using model predictive control. We considered simulated environments with static obstacles, but FaSTrack has been demonstrated in hardware to safely navigate around environments with static obstacles \cite{fridovich2018} and moving human pedestrians \cite{fisac2018probabilistically}.

There are still challenges and simplifications to address. The offline computation can be computationally prohibitive, a challenge we are working to address using techniques such as HJ reachability decomposition \cite{Chen2016DecouplingJournal,Chen2016DecouplingApprox}, sophisticated optimization techniques \cite{SinghChenEtAl2018}, and approximate dynamic programming \cite{royo2018classification}.  We are also interested in exploring methods to reduce conservativeness of the TEB by relaxing the worst-case assumption on the goals of the planning control.  Additionally, identifying when a particular tracking-planning model will have a converged value function remains an open question.  Finally, we currently assume both perfect sensing and a perfectly representative tracking model.  We would like to alleviate these assumptions by bounding uncertainty from sensing error, and making online updates to the value function as information about the tracking model is improved.

By computing trajectory-independent TEB, our framework decouples robustness guarantees from planning, and achieves the best of both worlds -- formal robustness guarantees which is usually computationally expensive to obtain, and real-time planning which usually sacrifices robustness.
Combined with any planning method in a modular fashion, our framework enables guaranteed safe planning and replanning in unknown environments, among other potential applications.