% !TEX root = tracking.tex
\section{Online Computation \label{sec:online}}
\begin{algorithm}	
  \smaller
	\caption{Online Trajectory Planning}
	\label{alg:algOnline}
	\begin{algorithmic}[1]
		%\STATE Inputs: tracking error function $\valfunc(\rstate)$, safety control function $\deriv(\rstate)$
		\STATE \textbf{Initialization}: \label{ln:Istart}
		\STATE $\tstate = 0$
		\STATE $\pstate = p_{start}$
		\STATE $\rstate = \tstate-\ptmat\pstate$
		\STATE $\TEB_\pstate(\tstate) = \{\pstate: \valfunc_\infty(\rstate) \le \underline\valfunc\}$
		 \label{ln:Iend}
		
		\WHILE{planning goal is not reached}
		\STATE \textbf{Tracking Error Bound Block}: \label{ln:obsStart}
		\STATE $\obsAug \leftarrow \obsSense + \TEB_\pstate(\tstate)$ \label{ln:obsEnd}
		
		\STATE \textbf{Path Planner Block}:\label{ln:plannerStart}
		\STATE $\pstate^+ \leftarrow \plannerfunc(\pstate, \obsAug)$\label{ln:plannerEnd}
		
		\STATE \textbf{Hybrid Tracking Controller Block}:\label{ln:controllerStart}
		\STATE $\rstate^+ = \tstate - \ptmat\pstate^+$
		
		\IF{$\rstate^+$ is on boundary $\TEB_\pstate(\tstate)$} 
		\STATE {use safety controller: $\tctrl \leftarrow \tctrl^*$ in \eqref{eq:opt_ctrl}}
		\ELSE \STATE{use performance controller: } 
          \STATE{$\tctrl \leftarrow$ desired controller} \ENDIF \label{ln:controllerEnd}
		
		\STATE \textbf{Tracking Model Block}: \label{ln:trackingStart}
		\STATE apply control $\tctrl$ to vehicle for a time step of $\dt$, save next state as $\tstate^+$ \label{ln:trackingEnd}
		
		\STATE \textbf{Planning Model Block}:\label{ln:planningStart}
		\STATE $\pstate = \tpmat\tstate^+$
		\STATE check if $\pstate$ is at planning goal
		\STATE reset states $\tstate = \tstate^+, \rstate = 0$ \label{ln:planningEnd}
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}
Algorithm \ref{alg:algOnline} describes the online computation. The inputs are the tracking error function $\valfunc_\infty(\rstate)$ and the safety control look-up function $\deriv_\infty(\rstate)$. Note that when discretized these functions will be look-up tables; practical issues arising from sampled data control can be handled using methods such as \cite{Mitchell2012, Mitchell13, Dabadie2014} and are not the focus of our paper.

Lines \ref{ln:Istart}-\ref{ln:Iend} initialize the computation by setting the tracking model state to zero and the planning model state to $p_{start}$, a state chosen to be within $\TEB$. The tracking error bound in the planning frame of reference is computed using (\ref{eq:TEBp}). Note that by initializing the planning state to be $p_{start}$ we can use the smallest possible invariant $\TEB_\pstate$ for the entire online computation. The tracking error bound block is shown on lines \ref{ln:obsStart}-\ref{ln:obsEnd}. The sensor detects obstacles $\obsSense$ within the sensing distance around the vehicle. The sensed obstacles are augmented by $\TEB_\pstate(\tstate)$ using the Minkowski sum. This is done to ensure that no unsafe path can be generated.\footnote{The minimum allowable sensing distance is $\senseDist = 2\TEB_\pstate(\tstate) + \dx$, where $\dx$ is the largest step in space that the planner can make in one time step.}

%\SHnote{The planning distance is the distance that the path planner (and thus the planning model) may take for each iteration of the online algorithm, and is chosen to be $0< \dx \leq \TEB$. This in turn determines the time step of each iteration (as shown on line \ref{ln:dt}): , where $v_{max}$ is the maximum speed of the planning model.}

 The path planner block (lines \ref{ln:plannerStart}-\ref{ln:plannerEnd}) takes in the planning model state $\pstate$ and the augmented obstacles $\obsAug$, and outputs the next state of the planning system $\pstate^+$. The hybrid tracking controller block (lines \ref{ln:controllerStart}-\ref{ln:controllerEnd}) first computes the updated relative state $\rstate^+$. If the $\rstate^+$ is on the tracking bound $\TEB_\pstate(0)$, the safety controller must be used to remain within the safe bound. The safety control is given by:
\begin{equation}
  \label{eq:opt_ctrl}
	\tctrl^* = \arg\min_{\tctrl\in\tcset} \max_{\pctrl\in\pcset, \dstb\in\dset} \nabla\valfunc(\rstate^+) \cdot \rdyn(\rstate^+,\tctrl,\pctrl,\dstb)
\end{equation}
For many practical systems (such as control affine systems), this minimization can be found extremely quickly. If the relative state is not on the tracking boundary, a performance controller may be used. For the example in Section \ref{sec:results} the these controllers are identical, but in general the performance controller can suit the needs of the individual applications.

The control $\tctrl^*$ is then applied to the physical system in the tracking block (lines \ref{ln:trackingStart}-\ref{ln:trackingEnd}) for a time period of $\dt$. The next state is saved as $\tstate^+$. We repeat this process until the planning goal has been reached.